Brownian Dynein Model

### 2015-07-22 latex/derivation.tex
clean up last equation two ways

$$
\hspace*{-4cm} \dot{\Theta}_{mr} =
$$
$$
\hspace*{-7cm} \frac{ \Big (\mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} - R_{ybr} - \frac{1}{\gamma}F_{ybr} \Big ) (Y_{mr} - Y_{t }) - \Big (L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} - \dot{X}_{t } - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} - \frac{1}{\gamma}F_{xbr} \Big ) (X_{mr} - X_{t })}
{L_{s}\sin(\Theta_{mr}-\pi)(X_{mr} - X_{t }) + L_{s}\cos(\Theta_{mr}-\pi)(Y_{mr} - Y_{t })}
$$

>>>>

\begin{multline}
\dot{\Theta}_{mr} =
\Bigg( \left(\mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} +
  \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -
  R_{ybr} - \frac{1}{\gamma}F_{ybr} \right) (Y_{mr} - Y_{t })
  \\
  - \left(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} - \dot{X}_{t }
          - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -
          \frac{1}{\gamma}F_{xbr} \right) (X_{mr} - X_{t })
          \Bigg) \\
/ \left(L_{s}\sin(\Theta_{mr}-\pi)(X_{mr} - X_{t }) + L_{s}\cos(\Theta_{mr}-\pi)(Y_{mr} - Y_{t })\right)
\end{multline}
or alternatively
\begin{multline}
\dot{\Theta}_{mr} =
\frac{ \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} +
  \dot{Y}_{t } - R_{ymr} - \frac{1}{\gamma}F_{ymr} + \dot{Y}_{mr} -
  R_{ybr} - \frac{1}{\gamma}F_{ybr}
}{
  L_{s}\sin(\Theta_{mr}-\pi)\frac{X_{mr} - X_{t}}{Y_{mr} - Y_{t }} +
  L_{s}\cos(\Theta_{mr}-\pi)
}
  \\
  - \frac{L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} - \dot{X}_{t }
          - R_{xmr} - \frac{1}{\gamma}F_{xmr} + \dot{X}_{mr} - R_{xbr} -
          \frac{1}{\gamma}F_{xbr}
          }{
 L_{s}\sin(\Theta_{mr}-\pi) +
L_{s}\cos(\Theta_{mr}-\pi)\frac{Y_{mr} - Y_{t }}{X_{mr} - X_{t }}
}
\end{multline}
